Public Security Concern: Bicycle Theft in Toronto Shows a Seasonal and Geographical Pattern

### 2023-11-05 outputs/paper/paper.qmd
Update introduction and reference

The remainder of this paper is structured as follows: @sec-data discusses the data with @sec-data_introduction includes basic information about data collection, and discussion about biases and ethical concerns about the data, @sec-data_cleaning includes packages used to clean the data and cleaning process with information about variables of interest, and @sec-data_analysis includes graphs and tables representing relationships between variables, and some discussions about implications.

@@

The dataset used in this analysis was obtained from Toronto's Open Data Portal and can be accessed from the package `opendatatoronto` [@citeOpendatatoronto]. The dataset `Bicycle Thefts` includes all bicycle theft occurrences reported to the Toronto Police Service from 2014 to 2022 [@citeData]. We use the latest `csv` version refreshed on Apr 4, 2023 in this analysis.

Since the occurrence of bicycle theft was self-reported, the reporter may choose to hide or inaccurately report some information and contributes to the reporting biases[@citeTorontopoliceservice]. Also, the location information is blurred due to privacy consideration.

## Data cleaning {#sec-data_cleaning}

We will use `R` to do the analysis in this report [@citeR]. After acquiring the dataset from package `opendatatoronto`[@citeOpendatatoronto], we used package `tidyverse`[@citeTidyverse] and package `janitor`[@citeJanitor] to clean the data and select variables for further analysis.

@@

* occ_year: Year offence occurred

* occ_month: Month offence occurred

* occ_date: Date offence occurred

* report_date: Date offence reported

* premises_type: Premises type of offence

* status: Whether the bicycle is recovered, stolen, or unknown

@@

* occ_year: Year offence occurred

* occ_month: Month offence occurred

* difference: Difference in days between occurrence date and report date

* location: Premises type of offence

* bicycle_status: Whether the bicycle is recovered, stolen, or unknown

## Data analysis {#sec-data_analysis}

@@

```{r}
#| label: fig-yearly_count_by_month
#| fig-cap: Bar plot of monthly number of occurrence of bicycle theft in Toronto for each year from 2014 to 2022
#| echo: false
#| warning: false
#| message: false

data |> ggplot(aes(x=occ_year, fill=occ_month)) +
  geom_bar() +
  labs(x = "Occurrence Year", y = "Number of occurrence", fill = "Occurrence Month") +
  scale_x_discrete() +
  theme_classic()
```

@@

```{r}
#| label: fig-location_count_by_year
#| fig-cap: Bar plot of number of occurrence of bicycle theft in difference type of location in Toronto for each year from 2014 to 2022.
#| echo: false
#| warning: false
#| message: false

>>>>

The remainder of this paper is structured as follows: @sec-data discusses the data with @sec-data_introduction includes basic information about data collection and cleaning results, and @sec-data_visualization includes graphs and tables representing relationships between variables and some discussions.

@@

The dataset used in this analysis was obtained from Toronto's Open Data Portal and can be accessed from the package `opendatatoronto` [@citeOpendatatoronto]. The dataset `Bicycle Thefts` includes all bicycle theft occurrences reported to the Toronto Police Service from 2014 to 2022 [@citeData]. Since the occurrence of bicycle theft was self-reported, there may exist reporting bias that the reporter may choose to hide or inaccurately report some information [@citeTorontopoliceservice]. Also, the location information is blurred due to privacy consideration.  We use the latest `csv` version refreshed on Apr 4, 2023 in this analysis.

We will use `R` to do the analysis in this report [@citeR]. After acquiring the dataset from package `opendatatoronto` [@citeOpendatatoronto], we used package `tidyverse` [@citeTidyverse] and package `janitor` [@citeJanitor] to clean the data and select variables for further analysis.

@@

* `occ_year`: Year offence occurred

* `occ_month`: Month offence occurred

* `occ_date`: Date offence occurred

* `report_date`: Date offence reported

* `premises_type`: Premises type of offence

* `status`: Whether the bicycle is recovered, stolen, or unknown

@@

* `occ_year`: Year offence occurred

* `occ_month`: Month offence occurred

* `difference`: Difference in days between occurrence date and report date

* `location`: Premises type of offence

* `bicycle_status`: Whether the bicycle is recovered, stolen, or unknown

## Data visualization {#sec-data_visualization}

@@

```{r}
#| label: fig-yearly_count_by_month
#| fig-cap: Monthly number of occurrence of bicycle theft in Toronto for each year from 2014 to 2022
#| echo: false
#| warning: false
#| message: false

data |> 
  mutate(occ_month = factor(occ_month, levels = month.name)) |> 
  ggplot(aes(x=as.factor(occ_year), fill=occ_month)) +
  geom_bar() +
  labs(x = "Occurrence Year", y = "Number of occurrence", fill = "Occurrence Month") +
  theme_minimal()
```

@@

```{r}
#| label: fig-location_count_by_year
#| fig-cap: Number of bicycle theft in different type of location in Toronto for each year from 2014 to 2022.
#| echo: false
#| warning: false
#| message: false
